---
title: "The parliamentary discourse on citizenship in Germany between 1996 and 2016"
subtitle: "Analysis"
author: "Examinee: Kevin Glock"
advisor: "Professor Andreas Blätte"
advisor2: "Merve Schmitz-Vardar, M.A."
date: "4 Juni 2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Appendix - Analysis


-------------------------------------------------------------------------------------------
!-- Third file Analysis.html.
-------------------------------------------------------------------------------------------


-------------------------------------------------------------------------------------------
## Contents
-------------------------------------------------------------------------------------------


* Analysis

  + long-term analysis of term frequencies on citizenship
  + parties` ideological argumentation


-------------------------------------------------------------------------------------------
## Analysis
-------------------------------------------------------------------------------------------

The corpus lingustical analysis on citizenship discourse is parted in three steps.
The first step includes the macro effects of immigration rate. By analysing the correlation between immigration rate and term frequencies on _Bundesebene_.
Secondly, contextualisation and argumentation on citizenship will be analysed on _Länderebene_ by using cooccurrence analysis.
Further a classification scheme will be outworked.

-------------------------------------------------------------------------------------------
## long-term analysis
-------------------------------------------------------------------------------------------


- Salience of immigration


-------------------------------------------------------------------------------------------
## long-term analysis
-------------------------------------------------------------------------------------------

Given keywords from the dictionary will be used for analysing the salience effect on speech frequencies regarding to citizenship.
In comparing the immigration rate statistics with the frequency of tokens, correlation can be tested. </p>
The immigration rate statistics come from the Federal Statitical Office of Germany (_Statistisches Bundesamt_).

-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}

library(xts)

dis <- dispersion("GERMAPARL",
                query = '".*([Oo]ption.|[Dd]oppel.)(modell|.bürger).*"',
                cqp = TRUE,
                s_attribute = c(
                  "year",
                  "party")
                )
```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}

ts <- xts(x = dis[,
                  c(
  "CDU", "SPD", "GRUENE",
  "FDP", "LINKE")
  ],
  order.by = as.Date(
    sprintf(
      "%s-01-01",
      dis[["year"]])
    )
  )

head(ts)

```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}

plot.xts(
  ts,
  col = c(
    "black", "red", "green",
    "yellow", "darkred"),
  multi.panel = F,
  lwd = 2,
  yaxs = "r"
)
```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}
library(xts)

citizendisp2 <- dispersion(
  "GERMAPARL",
  query = '"[Dd]oppelt.*" "[sS]taatsbürger.*"',
  cqp = TRUE,
  s_attribute = c("year"),
  freq = TRUE
  )

```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}
barplot(
  height = citizendisp2[["freq"]] * 100000,
  names.arg = citizendisp2[["year"]],
  las = 2,
  ylab = "Treffer pro 100.000 Worte"
  )

```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}

citizendisp3 <- dispersion(
  "GERMAPARL",
  query =  '"[Ss]taatsbürger.*"',
  cqp = TRUE,
  s_attribute = c(
    "year",
    "party")
  )

```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}
ts <- xts(x = citizendisp3[,
                           c(
                             "CDU", "CSU", "FDP",
                             "GRUENE", "SPD")
                           ],
          order.by = as.Date(
            sprintf("%s-01-01",
                    citizendisp3[["year"]])
            )
          )

head(ts)
```


-------------------------------------------------------------------------------------------
## periodical salience
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}
plot.xts(
  ts,
  multi.panel = TRUE,
  col = c(
    "black", "blue", "yellow",
    "green", "red"),
  lwd = 2,
  yaxs = "r"
  )

```


-------------------------------------------------------------------------------------------
## parties´ ideological arguementation
-------------------------------------------------------------------------------------------


- political party difference and political power through percentage of seats (meso)


-------------------------------------------------------------------------------------------
## parties´ ideological arguementation
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}

kwic <- kwic(
  "GERMAPARL",
  query = '".*([Oo]ption.*|[Dd]oppel.*).*(bürger|modell).*"',
  left = 5, right = 5,
  cqp = TRUE,
  s_attributes = c(
    "date",
    "party")
)
```


-------------------------------------------------------------------------------------------
## parties´ ideological arguementation
-------------------------------------------------------------------------------------------


- coocurrences and collocations of words (micro)
- individual speech and significant differences between actors


-------------------------------------------------------------------------------------------
## parties´ ideological arguementation
-------------------------------------------------------------------------------------------


```{r, eval= TRUE, echo=TRUE, message= FALSE}

```


-------------------------------------------------------------------------------------------
# convergences
-------------------------------------------------------------------------------------------

